The Sloan Digital Sky Survey Spectroscopic Reduction Pipeline

### 2006-04-01 doc/paper/paper2d.tex
Checking in the plate statistics plot

>>>>

In this paper, we describe the details of the SDSS 2-d spectroscopic pipeline
(idlspec2d) including steps starting with processing of the raw CCD frames to final
flux calibration and spectral co-addition.  Downstream pipelines which
calculate redshifts, spectral types, emission and absorption line identification,
and velocity dispersions are described elsewhere.
As of writing the 2-d pipeline has been run successfully on all spectroscopic
data obtained in the course of the survey from February 28, 2000 (MJD 2451602) 
to June 15, 2005 (MJD 2453536).  Over this timespan, which includes public data 
releases EDR through DR5, SDSS obtained survey quality spectroscopic data on
1656 fiber pluggings (640 fibers each in 1575 unique plates).   
A total of 972,111 sky positions were targetted, with the following 
breakdown in the best matched spectral classification:  651920 galaxies, 
208054 stars, 112137 QSOs and 51300 sky spectra.

Mean exposure time per plate is 3914 seconds, and the median is 3302 seconds.
In Figure 1 we show three of the observing diagnostics, on the top is
the effective signal-to-noise of the whole plate normalized to 3600 second
exposure time, the median seeing in arcseconds and the rms guide probe offset
in arcseconds are shown below.  The abscissa is in days after Feb 26, 2000
(MJD 2451600).
